On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-02-23 MS.tex
Discussion: clarify mechanism, as requested

While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result. Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by individuals with low SLA \citep{Reich:1992wm, Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended. Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}. In another modelling study, the SLA optimising growth rate was found to decrease with plant size, because of cross connections with the amount of self-shading in the crown and the increase in support costs in larger plants \citep{King-1999}. In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.

For seedlings our study showed, as expected, a negative relationship between seed mass and relative growth rate (in mass or height or volume) for small plants, that dissipated as plants grew larger. This negative relationship arises because seedlings from larger seeds begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.

>>>>

A single feature of plant growth underpins to the patterns associated with SLA, wood density, and seed size: the decrease in the ratio of leaf area to support tissue biomass with increasing plant size. Size-dependent requirements for mechanical and hydraulic support result in a substantial decline in the ratio of leaf biomass to total biomass with increasing plant size. Hence, the ratio of biomass production to total biomass and therefore relative growth rate must decline with increasing plant size \citep{Givnish:1995ta, Enquist:2007ek}, resulting in lower relative growth rates for large seedlings of large-seeded species than for small seedlings of small-seeded species \citep[reviewed by][]{Turnbull:2012ew}. For seedlings our study showed, as expected, a negative relationship between seed mass and relative growth rate (in mass, height, or volume) for small plants, that dissipated as plants grew larger.

Increasing support costs also devalue the benefits of cheap leaf construction (low SLA), because as plant's grow larger, an increasing amount of total biomass production is devoted to building and maintaining support tissues \citep{Givnish:1995ta,King-2011}. The net result is that the growth advantage experienced by high SLA species at small sizes, dissapates among larger plants. While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result. Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by individuals with low SLA \citep{Reich:1992wm, Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended. Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}. In another modelling study, the SLA optimising growth rate was found to decrease with plant size, because of cross connections with the amount of self-shading in the crown and the increase in support costs in larger plants \citep{King-1999}. In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
